---
title: "CDFA APN edit"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**The purpose of this Rmarkdown document is to edit CDFA APNs so that they are in a format that can be matched to APNs in the Kern County Parcel shapefile attribute table.**

**Notes:**   

  * APNs are self-reported by farmers to the CDFA, and exist in a wide variety of formats in the CDFA database *so*,
  * Before reading CSVs into this Rmd document, the APN entry format was edited in Excel:
      * Each individual entry was seperated into their own columns (i.e. if two entries were entered into the same cell, they were seperated, maintaining the same row but ending up in individual columns, so that each cell contained no more than one entry)
      * If APN #s didn't have dashes, a dash was added between the 3 and 4 digit and between the 6 and 7 digit. 
      
  * This code uses a function stored in the "1_APN_edit.R" file to edited APNs. The function takes the original APN values and puts them into a '123-456-78' format to match the format of those in the Kern County Parcel shapefile attribute table
  * APN edit methods were evaluated on the number of matches made between CDFA APNs and Kern County Parcel data, and the accuracy of those matches based on comparison of the Permittee and Company columns, respectively. This comparison can be seen in the table FILL IN THE BLANK
  * In some instances, the Permittee and Company columns did not match. Further research showed that this was often the result of parent companies owning smaller companies i.e. Parent company Grimmway Farms which owns Crystal Organics, based on records available on the internet <https://www.scscertified.com/fff/viewsupplier.php?id=776>;<https://www.growingproduce.com/vegetables/grower-experienced-in-biocontrols-says-be-patient/>. 

**Output:**

* CSV files of CDFA original and edited APNs in R_input and R_output files 

---

```{r load_packages_and_data, message=FALSE}
library(tidyverse)
library(reshape2)
library(rgdal)

# Set working directory for For Claire's computer
# setwd("~/Projects/Organics/Working/organics_repo/Rmarkdown/")

# Bring in the function stored in the '1_APN_edit.R' script. If editing that function, 
# check the box that says 'source on save' to upload that latest version of the function 
# in this Rmarkdown document
source("../R/1_APN_edit.R") 
```

## Apply function to years 2013 to 2019. It was ultimately a little easier to manually work through each year than to apply a for-loop because the column indexes (apn_cols) were different for each year. 

#### 2013
```{r yr2013, message=FALSE}

# Read in csv that contains APNs for Kern County in 2013. Prior to being read in to this 
# Rmarkdown document, APNs may have been edited in excel in one or more of the following 
# ways: (1) if multiple  APNs in one cell, seperated into individual cells across multiple 
# columns, (2) dashes added to those numbers that didn't have them. If dashes were added I 
# always started counting from the left and added a dash after the 3rd number and after the 
# 6th number. Original versions of the APNs were kept for comparison
cdfa_2013_raw = read_csv("../R_input/CSV/CDFA/excel_edited_APNs/CDFA_excelAPNs_2013.csv")

# Define parameters for APN_edit function in a list of elements. These also could be defined 
# directly in the function arguments below. 
apn_params = list(id_cols = 1:2, # ID Column used to go from wide to long format
                  apn_cols = 19:72, # These are the APN columns what will be melted into one
                  col_names = c("orgID", "company","APN_index","original_apn"), # Column names of the new long table
                  year = 2013) # Year being evaluated

# Create output directories
# dir.create("../R_input/CSV/CDFA/final_APN/",recursive = T)
# dir.create("../R_output/CSV/CDFA/final_APN/",recursive = T)

# Use the APN_edit_fun() with the list of parameters for the 2013 APNs. 
cdfa_2013_final_df = APN_edit_fun(cdfa_2013_raw, # 2013 CDFA Dataframe
                                  id_cols = apn_params$id_cols, 
                                  apn_cols = apn_params$apn_cols, 
                                  col_names = apn_params$col_names, 
                                  year = apn_params$year)

rm(apn_params)
# The warning message refers to empty cells that results when APNs are separated by '-' into 
# multiple columns. Those that have fewer than the maximum number of ? receive NAs in 
# those columns. The warning is not problematic and does not effect those APN values. 
```
All subsequent years follow the same order of operations as those explained in the code chunk above for 2013. 


#### 2014
```{r yr2014, message=FALSE}
cdfa_2014_raw = read_csv("../R_input/CSV/CDFA/excel_edited_APNs/CDFA_excelAPNs_2014.csv")

apn_params = list(id_cols = 1:2,
                  apn_cols = 21:74, 
                  col_names = c("orgID", "company","APN_index","original_apn"),
                  year = 2014)

cdfa_2014_final_df = APN_edit_fun(cdfa_2014_raw, 
                                  id_cols = apn_params$id_cols, 
                                  apn_cols = apn_params$apn_cols, 
                                  col_names = apn_params$col_names, 
                                  year = apn_params$year)
rm(apn_params)
```


#### 2015
```{r yr2015}
cdfa_2015_raw = read_csv("../R_input/CSV/CDFA/excel_edited_APNs/CDFA_excelAPNs_2015.csv")

apn_params = list(id_cols = 1:2, 
                  apn_cols = 21:74, 
                  col_names = c("orgID", "company","APN_index","original_apn"),
                  year = 2015)

cdfa_2015_final = APN_edit_fun(cdfa_2015_raw, 
                               id_cols = apn_params$id_cols, 
                               apn_cols = apn_params$apn_cols, 
                               col_names = apn_params$col_names, 
                               year = apn_params$year)
rm(apn_params)
```


#### 2016
```{r yr2016, message=FALSE}
cdfa_2016_raw = read_csv("../R_input/CSV/CDFA/excel_edited_APNs/CDFA_excelAPNs_2016.csv")

apn_params = list(id_cols = 1:2, 
                  apn_cols = 21:74, 
                  col_names = c("orgID", "company","APN_index","original_apn"),
                  year = 2016)

cdfa_2016_final_df = APN_edit_fun(cdfa_2016_raw, 
                                  id_cols = apn_params$id_cols, 
                                  apn_cols = apn_params$apn_cols, 
                                  col_names = apn_params$col_names, 
                                  year = apn_params$year)
rm(apn_params)
```


#### 2017
```{r yr2017, message=FALSE}
cdfa_2017_raw = read_csv("../R_input/CSV/CDFA/excel_edited_APNs/CDFA_excelAPNs_2017.csv")

apn_params = list(id_cols = 1:2, 
                  apn_cols = 21:74, 
                  col_names = c("orgID", "company","APN_index","original_apn"),
                  year = 2017)

cdfa_2017_final_df = APN_edit_fun(cdfa_2017_raw, 
                                  id_cols = apn_params$id_cols, 
                                  apn_cols = apn_params$apn_cols, 
                                  col_names = apn_params$col_names, 
                                  year = apn_params$year)
rm(apn_params)
```


#### 2018
```{r yr2018, message=FALSE}
cdfa_2018_raw = read_csv("../R_input/CSV/CDFA/excel_edited_APNs/CDFA_excelAPNs_2018.csv")

apn_params = list(id_cols = 1:2, 
                  apn_cols = 13:35, 
                  col_names = c("orgID", "company","APN_index","original_apn"),
                  year = 2018)

cdfa_2018_final_df = APN_edit_fun(cdfa_2018_raw, 
                                  id_cols = apn_params$id_cols, 
                                  apn_cols = apn_params$apn_cols, 
                                  col_names = apn_params$col_names, 
                                  year = apn_params$year)

rm(apn_params)
```

#### 2019
```{r yr2017, message=FALSE}
cdfa_2019_raw = read_csv("../R_input/CSV/CDFA/excel_edited_APNs/CDFA_excelAPNs_2019.csv")

apn_params = list(id_cols = 1:2, 
                  apn_cols = 13:35, 
                  col_names = c("orgID", "company","APN_index","original_apn"),
                  year = 2019)

cdfa_2019_final_df = APN_edit_fun(cdfa_2019_raw, 
                                  id_cols = apn_params$id_cols, 
                                  apn_cols = apn_params$apn_cols, 
                                  col_names = apn_params$col_names, 
                                  year = apn_params$year)
rm(apn_params)
```
