---
title: "Kern County Parcel Shapefile -- CDFA table join on APN Field and CDFA TRS section ID"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**The purpose of this Rmarkdown document is to join CDFA tabular data to the Kern County Parcel shapefile. Two previous Rmarkdown documents prepared APNs for the join**

**Notes:** 

* This Rmarkdown document uses a function in the "2_KernCountyParcel_CDFA_join.R" file to join CDFA and Kern County Parcel data on their respective APN columns. See notes in that R script for more details about that function

**Output:**

* Shapefile of with CDFA data joined to Kern County Parcel shapefile attribute table by APN

---

#### 1. Load packages, function, and data
```{r load_packages, message=FALSE}
library(tidyverse) # For general data wrangling and operations on dataframes
library(rgdal) # GDAL for R. 
library(sf) # For simple features operations in R. Allows the attribute table of a shapefile to be converted to a dataframe structure while maintaining the geometry for easy data view and operations. 

# Set working directory for For Claire's computer
setwd("~/Projects/Organics/Working/organics_repo/Rmarkdown")

# Bring in function stored in the '3_KernCountyParcel_CDFA_join.R' script. If editing that 
# function, check the box that says 'source on save' to upload that latest version of the 
# function in this Rmarkdown document
source("../R/2_KernCountyParcel_CDFA_join.R")

# Read in Kern County Parcel data and transform Kern County Parcel data into the correct CRS for project. CA Teale Albers 2011
KernCoParcels <- readOGR("../R_input/spatial/Kern_Parcels_2017_Final/Kern_Parcels_2017_Final.shp") %>% 
  spTransform(., CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs "))

```

#### 2. Apply function that joins CDFA data to Kern County Parcel data on the APN field specified years: 2013 - 2017. 
```{r apply_function}

# Specify years 
yrs = 2013:2017

# Create output directory
dir.create("../R_output/spatial/CDFA_APN_parcels/", recursive = T)

# For more notes about this function see the .R file

for(i in yrs){
  
  KernCoParcel_CDFA_join(year = i, # Year index
                         kern_parcel_shp = KernCoParcels) # Shapefile to be used

  }


```

#### 3. Identify PLSS Sections that contain organic parcels (the next phase of this, finding WHICH parcels are organic, is in RMD 4)

## 1) Read in Kern County Parcels that matched to CDFA records based on the APN
```{r cdfa_apn_match}

# Specify years for function to be applied to
yrs = 2013:2017

### Kern County Parcels that matched with CDFA APNs
for(i in yrs){
  
  tmp = readOGR(paste0("../R_output/spatial/CDFA_APN_parcels/",i,"/cdfa_parcels_",i,".shp")) %>% 
    st_as_sf()
  
  assign(paste0("cdfa_parcels_",i),tmp)
  
  rm(tmp)
  
  }

```

## 2) Bring in Kern Sections shapefile
```{r PLSS_shapefile}

# Bring in Kern Sections shapefile
kern_sections = readOGR("../R_input/spatial/Kern_sections/Kern_15r.shp")%>% 
  spTransform(., CRS("+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +datum=NAD83 +units=m +no_defs ")) %>% 
  st_as_sf()

# Filter attribute table for necessary fields/columns
kern_sections_slct = kern_sections %>% 
  dplyr::select(AREA, MTRS)

# Create TRS column by trimming "m' off the beginning of the MTRS column values
kern_sections_slct$trs <- str_sub(kern_sections_slct$MTRS,2,9)
```

## 3) Read in CDFA PLSS csv, join to PLSS shapefile and write output shapefile
```{r CDFA_trs}

yrs = 2013:2017



for(i in yrs){
  
  outputfile=paste0("../R_output/spatial/CDFA_PLSS_sections/",i)
  dir.create(outputfile)
  
  # Read in CDFA data with the TRS codes pulled from the APN column
  cdfa_trs_df = read_csv(paste0("../R_input/CSV/CDFA/excel_edited_PLSS/cdfa_trs_",i,".csv")) %>% 
    dplyr::select("Company","t","r","s") %>% 
    filter(!is.na(t)|!is.na(r)|!is.na(s)) %>% 
    mutate(trs = paste0(t,r,s))
  
  # Get a count of how many times each TRS is repeated and how many unique codes there are
  cdfa_trs_summary = cdfa_trs_df %>%
    group_by(Company,trs) %>%
    summarise(count = n())
  
  print(i)
  print(table(cdfa_trs_summary$Company))
  
  # Merge CDFA to PLSS sections on the TRS columns created above
  cdfa_sections = merge(kern_sections_slct,cdfa_trs_df,by = "trs")
  
  # The merge produces some duplicate matches. This gets rid of them, then cleans up the data.frame and turns it back into a Spatial Polygons file
  cdfa_sections_unique = distinct(cdfa_sections,.keep_all = T) %>% 
    dplyr::select(trs,company = "Company",geometry) %>% 
    as(.,"Spatial")

  #Layer Name
  cdfalayer=paste0("cdfa_sections_",i)
  
  writeOGR(cdfa_sections_unique,
           dsn = outputfile,
           layer =cdfalayer,
           driver = "ESRI Shapefile",
           overwrite = TRUE)
  
  # Remove CDFA dataframes to make sure there isn't crossover between years
  
  rm(cdfa_sections)
  rm(cdfa_sections_unique)
  rm(cdfa_trs_summary)
  rm(cdfa_trs_df)
  
}

```





