---
title: "Kern County Agriculture -- CDFA parcel spatial join"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**The purpose of this Rmarkdown file is to join CDFA organic parcels (CDFA data matched to Kern County parcels on APN or TRS codes) to Kern County Agriculture parcels.**

**Notes:**

* CDFA parcels were determined by formatting APNs reported to the CDFA by growers, then matching the formatted APNs to Kern County Assessor Parcel spatial data on the APN field. 
* Kern County Agriculture parcels are available on the Kern County Website. 
* Polygons in the Kern County Agriculture shapefile and Kern County Parcel shapefile have different dimensions, with Kern Agriculture fields being generally smaller and containing more detailed agriculture information. This spatial join determines and extracts overlapping parcels and maintains the Kern County Agriculture shapefile's polygon dimensions, which gives us more detailed and accurate information about crop fields in Kern County.  
* This Rmarkdown document uses a function in the "4_KernAg_CDFA_Join.R" file. Function variables include:
       * Year (year)
       * Buffer width (buf_width)
       * Two true/false argument for function output


**Output:**

* The function output can be:
       * A joined shapefile that includes all AG parcels and the Kern Ag/CDFA attribute table
       (write_all_shp = TRUE)
       * A joined shapefile that is filtered to only include ag parcels that joined to a CDFA parcel
       (write_cdfa_shp = TRUE)
       
---


#### 1. Load packages, set working diretory, and source KernAg_CDFA_join.R file with contains a function that does a spatial join between the two data.sets
```{r packages_and_function}
library(tidyverse) # General data organization
library(rgdal) # Gdal for R
library(rgeos) # need this for gBuffer
library(sf) # Specific operations on different versions of shapefiles in R
library(raster)

setwd("~/Desktop/Organics_Final/Working/organics_repo/Rmarkdown")

# Access function in .R document used to join Kern Agriculture and CDFA parcel shapefiles. 
# See the .R file for more information about the function
source("../R/4_KernAg_CDFA_Join.R")
```

#### 2. Implement the function that performs a spatial join between APN-matched CDFA parcels and Kern Agriculture parcels for specific years and desired buffer width. See notes in the following code chunk for more information about buffer widths and how 50m was determined
```{r implement_function, message=FALSE, warning=FALSE}
# Years of interest
years = 2017

# Buffer widths: In the function these are negative and reduce the CDFA field size. 
# A larger buffer results in a more conservative spatial join between the CDFA parcels and 
# Kern County Agriculture Parcels. The fields in each shapefile have different dimensions, and 
# with no buffer applied CDFA fields match to Kern Ag parcels that hardly touch, increasing the 
# risk of false matches. 

# With a 100-meter buffer, the Kern Ag fields that CDFA parcels join to are almost entirely 
# within the CDFA parcels which results in a loss of reasonable matches.

# A 50-meter buffer provides conservative but seemingly accurate matches. 
# Matches were checked by comparing the company and permittee columns in the attribute 
# table of the resulting joined shapefile.

buf_width = c(50)

for(i in years){
  
  for(j in buf_width){
  
    # Create output directory for the output CSV file that lists the CDFA data 
    # with commodities from Kern Ag data attached
    dir.create(paste0("../R_output/CSV/CDFA_KernAg_join/",i),
               recursive = TRUE)
    
    # Create the output directory for the full CDFA_KernAg_join shapefile, no filters applied. 
    dir.create(paste0("../R_output/spatial/CDFA_KernAg_join/",i,"/buffer",j),
               recursive = TRUE)
    
    # Apply the function that is in the KernAg_CDFA_Join.R script
    kernAg_CDFA_joinFun(i, buf_width = j, write_all_shp = T, write_cdfa_shp = T)
 
     }
  }

```


#### 3. Perform spatial join between CDFA TRS-matched sections and Kern Agriculture Parcels -- Extract Ag parcels that overlap with CDFA sections AND contain the word 'organic' in the company name. 
```{r trs_ag_join}

# Read in data produced above. This is the cdfa data joined to kern county parcels on APN, then spatially joined to kern ag data in the above function
kernAg_cdfa_APN <- readOGR("../R_output/spatial/CDFA_KernAg_join/2017/buffer50/KernAg_CDFA_all_2017_B50.shp") %>% 
  st_as_sf()

# Read in Kern Ag with Soil info shapefile
kernAg <- readOGR("../R_output/spatial/KernAg_withSoil/2017/KernAg_withSoil_2017.shp") %>% 
  st_as_sf()

# Get rid of unnecessary Kern ag columns
kernAg_select = kernAg %>% 
  dplyr::select(PERMIT,SITEID,S_STATUS,COMM,PMT_SITE,PERMITTEE,ACRES,soil)

# Read in shaepfile of the PLSS Sections that joined to CDFA data on TRS codes. 
# Two producers used TRS codes instead of APNs, which is where TRS was pulled from 
cdfa_sections <- readOGR("../R_output/spatial/CDFAtrs_sections/cdfa_sections.shp") %>% 
  st_as_sf() %>% 
  mutate(TRS_match = 1)

# Spatial join between kern ag parcels and cdfa sections, maintain the shape of the kern ag polygons
kernAg_sections_join <- st_join(kernAg_select,cdfa_sections,largest=T)

# Filter above spatial join ouput for the parcels that: (1) Matched a PLSS Section TRS code with CDFA TRS code (2) Succesfully joined to an Ag parcel and (3) contained the word "ORGANIC" in the Permittee column

kernAg_cdfa_TRS = st_as_sf(kernAg_sections_join) %>% # Convert into a simple features DF
  filter(str_detect(PERMITTEE,"ORGANIC") & !is.na(trs)) %>% # Filter for the word 'Organic' in the permittee column
  dplyr::select("permittee" = PERMITTEE,
               company,
               "trs_match" = TRS_match)


## 298

# Join TRS section data to Kern Ag/CDFA_APN data. 
cdfa_APNtoTRS_join <- st_join(kernAg_cdfa_APN,
                                 kernAg_cdfa_TRS,
                                 largest=T,
                                 suffix = c(".apn",".trs"))

# Filter data.frame to remove joins that seem false (permittee columns not equal)
APNtoTRS_joinFilter = cdfa_APNtoTRS_join %>% 
  filter(permittee == PERMITTEE|is.na(permittee)) # This filter removes spatial joins in which the permittee columns do not match, indicating a false join. It removes a total of 17 fields, or 0.15% of the total fields

# Clean up dataframe before export
APNtoTRS_joinFinal <- APNtoTRS_joinFilter %>% 
  dplyr::select("permitsite" = PMT_SITE,
         "s_status" = S_STATUS,
         "permittee" = PERMITTEE,
         "comm_grp"=COMM_GROUP,
         "comm" = COMM,
         "comm_edit"=COMM_new,
         "acres"=ACRES,
         "soil_q"=SOILQ,
         "apn_match"=CDFA,
         trs_match)

# Replace NAs with 0s in the trs_match column
APNtoTRS_joinFinal$trs_match <- ifelse(is.na(APNtoTRS_joinFinal$trs_match),0,APNtoTRS_joinFinal$trs_match)

# Create a binary organic column based on the apn_match and trs_match columns. If either of those indicates that the parcel is organic then the value in the binary organic column == 1.
APNtoTRS_joinFinal$organic <- ifelse(APNtoTRS_joinFinal $apn_match==1|APNtoTRS_joinFinal$trs_match==1,1,0)

# Write Output File
writeOGR(obj = as(APNtoTRS_joinFinal,"Spatial"),
         dsn = "../R_output/spatial/CDFA_KernAg_join/2017/buffer50/",
         layer = "TRSandAPN_organics",
         driver = "ESRI Shapefile",
         overwrite_layer = T)


```

