---
title: "Join PesticideUseData to Finazlied Organic Parcel Shapefile for all years"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**The purpose of this Rmarkdown file is to join pesticide use data to the Kern County Agriculture-CDFA shapefile finalized in RMD 4**  


**Notes:**

- In code chunk 5, this document also determines the number of crops being grown on each field. This helps us prevent bias that may arise from fields that have multiple crops [S_STATUS == "M"].

**Output:**
- Shapefile that includes information from Kern Ag, CDFA, Storie Index (soil), and pesticide use data in the attribute table
      - ../R_output/spatial/final_organics_data/[YEAR]/all_organics_pest_[YEAR].shp

---


#### 1. Get Packages and Data
```{r get_packages_and_data}
library(haven)
library(tidyverse)
library(rgdal)
library(sf)

# Avoid scientific notation
options(scipen = 999) 

# Read in Pesticide Data 
pest_data_raw = read_dta("../R_input/dta/KernOrgCollapse1319_062620.dta") %>% 
  as.data.frame() 

# Specify years of interest
years = 2013:2019

# Specify buffer width -- Buffer widths were originally implemented in the Kern Agriculture CDFA Parcel spatial join (RMD 4). 
buf_width = c(50)
```


#### 2. Create pesticide use dataframes for each year from original compiled data set
```{r pest_dataframes, message=FALSE}

#### For loop to create dataframes of pesticide use for each year from 2013:2019
for(i in years){ 
  
  # Filter pesticide data year i
  tmp <- filter(pest_data_raw,year==i)
  
  # Give it a name for that specific year
  assign(paste0("pest_data_",i),tmp)
  
  }

# # Uncomment to see number of distinct permitsite-commodity combinations in each year. Should be the same as the number of rows in the data setfor each year
# nrow(pest_data_2013)
# n_distinct(pest_data_2013$permitsite,pest_data_2013$commodity)
# # PS_dups_13 = as.data.frame(table(pest_data_2013$permitsite,pest_data_2013$commodity)) %>% filter(Freq>1) %>% mutate(year = 13)
# 
# nrow(pest_data_2014)
# n_distinct(pest_data_2014$permitsite, pest_data_2014$commodity)
# # PS_dups_14 = as.data.frame(table(pest_data_2014$permitsite, pest_data_2014$commodity)) %>% filter(Freq>1) %>% mutate(year = 14)
# 
# nrow(pest_data_2015)
# n_distinct(pest_data_2015$permitsite,pest_data_2015$commodity)
# # PS_dups_15 = as.data.frame(table(pest_data_2015$permitsite)) %>% filter(Freq>1) %>% mutate(year = 15)
# 
# nrow(pest_data_2016)
# n_distinct(pest_data_2016$permitsite,pest_data_2016$commodity)
# # PS_dups_16 = as.data.frame(table(pest_data_2016$permitsite)) %>% filter(Freq>1) %>% mutate(year = 16)
# 
# nrow(pest_data_2017)
# n_distinct(pest_data_2017$permitsite,pest_data_2017$commodity)
# # PS_dups_17 = as.data.frame(table(pest_data_2017$permitsite)) %>% filter(Freq>1) %>% mutate(year = 17)
# 
# nrow(pest_data_2018)
# n_distinct(pest_data_2018$permitsite,pest_data_2018$commodity)
# # PS_dups_18 = as.data.frame(table(pest_data_2018$permitsite)) %>% filter(Freq>1) %>% mutate(year = 18)
# 
# nrow(pest_data_2019)
# n_distinct(pest_data_2019$permitsite,pest_data_2019$commodity)
# # PS_dups_19 = as.data.frame(table(pest_data_2019$permitsite)) %>% filter(Freq>1) %>% mutate(year = 19)
# 
# # PS_dups = rbind(PS_dups_13,PS_dups_14,PS_dups_15,PS_dups_16,PS_dups_17)
# # colnames(PS_dups) = c("permitsite","n_dups","year")
```

#### 3. Read in KernAg_CDFA shapefiles for each year and give unique name
```{r get_kernAg}

# Read in KernAg_CDFA (joined) shapefile with appropriate buffer and convert to spatial dataframe

for(i in years){ # For each year...
  for(j in buf_width){ # And each buffer width...
  
  # Read in the joined KernAg_CDFA data...
  tmp <- read_sf(paste0("../R_output/spatial/final_organics_data/",i,"/all_organics_",i,".shp")) 

  
  # Assign a name
  assign(paste0("organics_",i,"_B",j),tmp)
  print(c(i,nrow(tmp)))
  remove(tmp)
    }
}

# Uncomment to fix the commodity column in '18 and '19 where the word "ORGANIC" is truncated in some cells, which effects the permitsite/comm join in the following code chunk
organics_2018_B50$comm = as.character(organics_2018_B50$comm)
organics_2018_B50 <- separate(organics_2018_B50,comm,into = c("comm","suf"),sep = "-")
organics_2018_B50$suf = ifelse(str_detect(string = organics_2018_B50$suf, pattern = "OR"), "ORGANIC", organics_2018_B50$suf)
organics_2018_B50$comm = ifelse(!is.na(organics_2018_B50$suf),paste0(organics_2018_B50$comm,"-",organics_2018_B50$suf),organics_2018_B50$comm)
organics_2018_B50 = dplyr::select(organics_2018_B50, -suf)

organics_2019_B50$comm = as.character(organics_2019_B50$comm)
organics_2019_B50 <- separate(organics_2019_B50,comm,into = c("comm","suf"),sep = "-")
organics_2019_B50$suf = ifelse(str_detect(string = organics_2019_B50$suf, pattern = "OR"), "ORGANIC", organics_2019_B50$suf)
organics_2019_B50$comm = ifelse(!is.na(organics_2019_B50$suf),paste0(organics_2019_B50$comm,"-",organics_2019_B50$suf),organics_2019_B50$comm)
organics_2019_B50 = dplyr::select(organics_2019_B50, -suf)

```


#### 4. Join pesticide data to Kern Agriculture/CDFA data by the 'permitsite' column. The 'permitsite' column is the unique identifier for each field, and is a concatenated version of the permit number and site ID. 
```{r warning=FALSE}
for(i in years){
  
  # Find the Kern Ag-CDFA data.frame that was previously read in and corresponds 
  # to year.i and buffer_width.j
  tmp_ag = eval(as.name(paste0("organics_",i,"_B",j)))  %>% 
    as.data.frame() 
  
  colnames(tmp_ag)[2] <- "permitsite"
  colnames(tmp_ag)[6] <- "commodity"
  
  # Check to make sure all permits are 7 characters long -- check all years in RMD 6 and true: all permits = 7 characters long
  # nchars = as.data.frame(table(nchar(tmp_ag$permit)))
  
  # Get tmp copy of the pesticide use data.frame that corresponds to pest_data_year.i
  tmp_pst = eval(as.name(paste0("pest_data_",i)))
  
  # Left join the pesticide use data.frame to the Agriculture shapefile on 'permitsite' and 'commodity' -- use this to data.frame to filter out fuzzy joins
 left_joined_ag_pst = left_join(tmp_ag,tmp_pst, by = c("permitsite","commodity"), suffix = c(".ag", ".pur"))
 
 # find out how much of the pest data didn't have an ag match
 anti_joined_pst = anti_join(tmp_pst,tmp_ag, by = c("permitsite","commodity"), suffix = c(".ag", ".pur"))
 print(c(i,"anti_joined_pst",nrow(anti_joined_pst)))
   # 2013: 51
   # 2014: 37
   # 2015: 66
   # 2016: 80
   # 2017: 66
   # 2018: 85
   # 2019: 99
 
  # Find out how much of the ag data didn't have a pest match
  anti_joined_ag = anti_join(tmp_ag,tmp_pst, by = c("permitsite"), suffix = c(".ag", ".pur"))
  print(c(i,"anti_joined_ag", nrow(anti_joined_ag)))
   # 2013: 3951
   # 2014: 4187
   # 2015: 4184
   # 2016: 4165
   # 2017: 4068
   # 2018: 4242
   # 2019: 4190
  
  # Assign a unique name based on the year
  assign(paste0("organics_pest_",i), left_joined_ag_pst)
  
}

```

#### 5. Determine the number of crops being grown on multi-crop fields (s_status == "M") and add information to the KernAg_CDFA_pesticideUse dataframe shapefile.
```{r deal_with_Mfields, warning=FALSE}

for(i in years){
  
  tmp_orgs_df = eval(as.name(paste0("organics_pest_",i)))
      
  # Turn the kernAg_CDFA_pest shapefile into a simple features (spatial) data.frame
      M_status_df = tmp_orgs_df %>% 
        # Turn into basic data.frame to remove spatial references
        as.data.frame() %>% 
        # Select columns relevant to dealing with M fields
        dplyr::select(permitsite,s_stats)
  
      # Create a new column of permitsites with the last character trimmed from each 
      # 'permitsite' string that correspond to a field with an "M" in the "S_STATUS" column.

      # For rows with "M" in column "S_STATUS"
      M_status_df$permitsite_trim1 = ifelse(M_status_df$s_stats == "M", 
          
        # Trim the last character off the 'permitsite' string
        strtrim(M_status_df$permitsite,width=nchar(M_status_df$permitsite)-1),
    
        # Leave other rows alone
        M_status_df$permitsite)
    
      
      # Create another new column from the original "permitsite" field with only the last character 
      # from the string. This is used to double check the seperation of characters in the step above. If concatenated,
      # '_trim1' + '_trim2' should be identical to the original 'permitsite' string.  
      
      # If the value in 'S_STATUS' == M
      M_status_df$permitsite_trim2 = ifelse(M_status_df$s_stats == "M",
                                     
           # Grab the last character in the 'permitsite' string
           substr(x = M_status_df$permitsite,
           start = nchar(M_status_df$permitsite),
           stop = nchar(M_status_df$permitsite)), 
        
           # Otherwise make equal to NA
           NA)

      
      # Create a new dataframe that has each unique 'permitsite' string in the first column
      # and the number of times it is repeated in the second column. Multi-crop fields (S_STATUS == M) 
      # are consistently distinguised from one another by a unique character at the end (right side) 
      # of an otherwise identical 'permitsite' string. With the last character trimmed off of those strings, 
      # we can determine the number of crops in the multi-crop fields based on the number of duplicate
      # permitsites in the 'permitsite_trim1' column.
      prmtst_duplicates = as.data.frame(table(M_status_df$permitsite_trim1))
      
      
      # Rename columns from generic names given by table() function
      colnames(prmtst_duplicates) = c('permitsite','n')
      
      # Merge multicrop_df data.frame (with permitsite_trim columns) and prmtst_dups data.frame. This merge 
      # allows us to see how many crops are associated with each permitsite i.e. how many 
      # crops are in each individual field. 
      M_status_df_final = merge(M_status_df, 
                                 prmtst_duplicates, 
                                 by.x="permitsite_trim1", 
                                 by.y="permitsite", 
                                 type = "right") %>% 
        dplyr::select(permitsite,n)
      
      # Rename columns for merge and later use
      colnames(M_status_df_final) = c("permitsite","N_crops_prmtst")
      
      # Merge the final multicrop_df dataframe into the tmp_orgs_df_final simple features data.frame
      orgs_df_final = merge(tmp_orgs_df, M_status_df_final, by = 'permitsite')
      
      # Remove extra dataframes that could accidentally carry into other years
      remove(M_status_df_final,prmtst_duplicates,M_status_df,tmp_orgs_df)
      
      # Convert the acres column to numeric
      orgs_df_final$acres = as.numeric(as.character(orgs_df_final$acres))
      
      # create a 'hectares' column using the 'acres' column
      orgs_df_final$hectares = orgs_df_final$acres*0.405/orgs_df_final$N_crops_prmtst
      
      # Create a kilograms of active ingredients per hectare column
      # orgs_df_final$kgAIperhec = orgs_df_final$KgPestAI/orgs_df_final$hectares
      # orgs_df_final$kgPrdPerHe = orgs_df_final$KgPestPrd/orgs_df_final$hectares
      
      # Remove the "permitno" and "location" columns
      # orgs_df_final = orgs_df_final %>% 
      #   select(-c("permitno","location"))
      
      # Save in global environment
      assign(paste0("organics_df_final_",i), orgs_df_final)
      
        # Write the shapefile in to the output directory
        writeOGR(as(st_as_sf(orgs_df_final),"Spatial"),
                 paste0("../R_output/spatial/final_organics_data/",i),
                 paste0("all_organics_pest_",i),
                 driver = "ESRI Shapefile",
                 overwrite_layer = TRUE)
        
}

```




