---
title: "7. Final Summary Table"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**The purpose of this Rmarkdown file is to create summary tables from the final dataset from RMD 6.**  

**Input:**
../R_input/dta/organicAnalysisPUR copy.dta


**Output:**
- ../R_output/CSV/organicVSconventional_summarytable.csv
- ../R_output/CSV/organicVSconventional_SIsummarytable.csv

---

```{r packages}

library(tidyverse)
library(haven)
# library(pastecs)
options(scipen = 9999)

rm(list=ls())
```


```{r data}
### Read in dta file from Ashley -- output of RMD 6 with pesticide use info and IHS transformed data used in analyses added on
final_data = read_dta("../R_input/dta/organicAnalysisPUR.dta") %>% as.data.frame()

```


# Building summary tables
## Main Text Summary Table for AI and PRD
```{r main_text_table}

# List of top 5 crops
# top5 = c("CARROT","GRAPE","ORANGE","ONION DRY ETC","POTATO")
top5commcodes =  c('29141','29111','14011','14013','2006')

# Build a summary table
all_crops = final_data %>% 
  mutate(kgAI_ha = KgPestAI/hectares, # kgAI per hectare
         kgPrd_ha = KgPestPrd/hectares) %>% # kg pest product per hectare
  group_by(pur_cdfa_org) %>% # Group by org/conventional
  summarise(total_fields = n(), # Count total fields (by groups)
            avg_fieldsz = mean(hectares), # Mean field size in hectares
            se_fieldsz = sd(hectares)/sqrt(length(hectares)), # SE for field size
            avg_soilq = mean(soil_quality, na.rm = T), # avg soil quality
            se_soilq = sd(soil_quality, na.rm = T)/sqrt(length(soil_quality[!is.na(soil_quality)])), # SE of mean soil quality
            avg_aihe = mean(kgAI_ha, na.rm=T), # Avg kg/hectare
            se_ai = sd(kgAI_ha, na.rm=T)/sqrt(length(kgAI_ha)), # SE kg per hectare
            avg_prdhe = mean(kgPrd_ha, na.rm=T), # Avg prd per hecatre
            se_prd = sd(kgPrd_ha, na.rm=T)/sqrt(length(kgPrd_ha))) %>% # SE prd per hectare 
  as.data.frame(.)

all_crops$category = "all_fields"

top5_summary = final_data %>% 
  mutate(kgAI_ha = KgPestAI/hectares,
       kgPrd_ha = KgPestPrd/hectares) %>% 
  filter(comm_code2 %in% top5commcodes) %>% # Filter for top 5 commodities
  group_by(comm_code2,pur_cdfa_org) %>% 
  summarise(total_fields = n(),
            avg_fieldsz = mean(hectares), 
            se_fieldsz = sd(hectares)/sqrt(length(hectares)), 
            avg_soilq = mean(soil_quality,na.rm = T), 
            se_soilq = sd(soil_quality, na.rm = T)/sqrt(length(soil_quality[!is.na(soil_quality)])), 
            avg_aihe = mean(kgAI_ha,na.rm=T),
            se_ai = sd(kgAI_ha,na.rm=T)/sqrt(length(kgAI_ha)),
            avg_prdhe = mean(kgPrd_ha,na.rm=T),
            se_prd = sd(kgPrd_ha,na.rm=T)/sqrt(length(kgPrd_ha))) %>% 
  as.data.frame(.)

colnames(top5_summary)[1] <- "category" # Rename category column
top5_summary <- top5_summary[,c(2:11,1)] # Reorder dataframe to do row bind below

summary_table_final = rbind(all_crops,top5_summary)
write_csv(summary_table_final, "../R_output/CSV/organicVSconventional_summarytable.csv" )

```

## SI table for AI PRD
```{r SI_table}

top5 = c("CARROT","GRAPE","ORANGE","ONION DRY ETC","POTATO")
top5commcodes =  c('29141','29111','14011','14013','2006')

# Building a summary table
all_crops = final_data %>% 
  mutate(kgAI_ha = KgPestAI/hectares,
         kgPrd_ha = KgPestPrd/hectares) %>% 
  group_by(pur_cdfa_org) %>% 
  summarise(total_fields = n(),
            avg_fieldsz = mean(hectares), # Mean field size in hectares
            se_fieldsz = sd(hectares)/sqrt(length(hectares)), # mean of average in he
            avg_soilq = mean(soil_quality,na.rm = T), # avg soil quality
            se_soilq = sd(soil_quality, na.rm = T)/sqrt(length(soil_quality[!is.na(soil_quality)])), # SE of mean soil quality
            avg_aihe = mean(kgAI_ha,na.rm=T),
            se_ai = sd(kgAI_ha,na.rm=T)/sqrt(length(kgAI_ha)),
            avg_prdhe = mean(kgPrd_ha,na.rm=T),
            se_prd = sd(kgPrd_ha,na.rm=T)/sqrt(length(kgPrd_ha))) %>% 
  as.data.frame(.)
all_crops$category = "all_fields"

top5_summary = final_data %>% 
  mutate(kgAI_ha = KgPestAI/hectares,
       kgPrd_ha = KgPestPrd/hectares) %>% 
  filter(comm_code2 %in% top5commcodes) %>% 
  group_by(comm_code2,pur_cdfa_org) %>% 
  summarise(total_fields = n(),
            avg_fieldsz = mean(hectares), # Mean field size in hectares
            se_fieldsz = sd(hectares)/sqrt(length(hectares)), # mean of average in he
            avg_soilq = mean(soil_quality,na.rm = T), # avg soil quality
            se_soilq = sd(soil_quality, na.rm = T)/sqrt(length(soil_quality[!is.na(soil_quality)])), # SE of mean soil quality
            avg_aihe = mean(kgAI_ha,na.rm=T),
            se_ai = sd(kgAI_ha,na.rm=T)/sqrt(length(kgAI_ha)),
            avg_prdhe = mean(kgPrd_ha,na.rm=T),
            se_prd = sd(kgPrd_ha,na.rm=T)/sqrt(length(kgPrd_ha))) %>% 
  as.data.frame(.)

colnames(top5_summary)[1] <- "category"
top5_summary <- top5_summary[,c(2:11,1)]

all_crops_that_spray = final_data %>%
  mutate(kgAI_ha = KgPestAI/hectares,
       kgPrd_ha = KgPestPrd/hectares) %>%
  filter(KgPestPrd>0) %>%
  group_by(pur_cdfa_org) %>%
  summarise(total_fields = n(),
            avg_fieldsz = mean(hectares), # Mean field size in hectares
            se_fieldsz = sd(hectares)/sqrt(length(hectares)), # mean of average in he
            avg_soilq = mean(soil_quality,na.rm = T), # avg soil quality
            se_soilq = sd(soil_quality, na.rm = T)/sqrt(length(soil_quality[!is.na(soil_quality)])), # SE of mean soil quality
            avg_aihe = mean(kgAI_ha,na.rm=T),
            se_ai = sd(kgAI_ha,na.rm=T)/sqrt(length(kgAI_ha)),
            avg_prdhe = mean(kgPrd_ha,na.rm=T),
            se_prd = sd(kgPrd_ha,na.rm=T)/sqrt(length(kgPrd_ha))) %>% 
  as.data.frame(.)

all_crops_that_spray$category = "all_fields_spray"
top5_that_spray = final_data %>%
  mutate(kgAI_ha = KgPestAI/hectares,
       kgPrd_ha = KgPestPrd/hectares) %>%
  filter(KgPestPrd>0) %>%
  filter(comm_code2 %in% top5commcodes) %>%
  group_by(comm_code2,pur_cdfa_org) %>%
  summarise(total_fields = n(),
            avg_fieldsz = mean(hectares), # Mean field size in hectares
            se_fieldsz = sd(hectares)/sqrt(length(hectares)), # mean of average in he
            avg_soilq = mean(soil_quality,na.rm = T), # avg soil quality
            se_soilq = sd(soil_quality, na.rm = T)/sqrt(length(soil_quality[!is.na(soil_quality)])), # SE of mean soil quality
            avg_aihe = mean(kgAI_ha,na.rm=T),
            se_ai = sd(kgAI_ha,na.rm=T)/sqrt(length(kgAI_ha)),
            avg_prdhe = mean(kgPrd_ha,na.rm=T),
            se_prd = sd(kgPrd_ha,na.rm=T)/sqrt(length(kgPrd_ha))) %>% 
  as.data.frame(.)

colnames(top5_that_spray)[1] <- "category"
top5_that_spray <- top5_that_spray[,c(2:11,1)]
top5_that_spray$category <- paste0(top5_that_spray$category,"_spray")

summary_table_final = rbind(all_crops,all_crops_that_spray, top5_summary, top5_that_spray)

write_csv(summary_table_final, "../R_output/CSV/organicVSconventional_SIsummarytable.csv" )

```

# Farm sizes
```{r farmsizes}

# Mean farm size across all years
farms = final_data %>% 
  group_by(year,permit) %>% 
  summarise(frmsize = sum(hectares),
            .groups='keep') %>% 
  group_by(permit) %>% 
  summarise(FS )

mean(farms$frmsize)

df = final_data %>% # Get all data
    filter(!is.na(soil_quality)) %>% 
    filter(family != "") %>% 
    group_by(permit,pur_cdfa_org,year) %>% # group by permit, org/conventional, year
    summarise(frmsize = sum(hectares),.groups='keep') # Find total farm size -- org and conventional portions separate here but combined later
  
# Exclude farms that have at least one organic field (purely org or conventional + org)
conv_only = df %>%
  group_by(permit,year) %>% 
  filter(!(any(pur_cdfa_org==1))) %>% 
  summarise(frmsize = sum(frmsize),.groups='keep')
  
# atleast_1org = df %>% # Get all data
#   group_by(permit,year) %>% # group by permit
#   filter(any(pur_cdfa_org==1)) %>% # Get permits that have at least one org
#   filter(!(all(pur_cdfa_org==1))) %>% # But remove purely organic permits (this removes crystal orgs)
#   summarize(frmsize = sum(frmsize),.groups='keep') # Find total farmsize (org + conventional) for each permit each year

atleast_1org = df %>% # Get all data
  group_by(permit,year) %>% # group by permit
  filter(any(pur_cdfa_org==1)) %>% # Get permits that have at least one org
  filter(!(all(pur_cdfa_org==1))) %>% # But remove purely organic permits (this removes crystal orgs)
  summarize(frmsize = sum(frmsize),.groups='keep') # Find total farmsize (org + conventional) for each permit each year

mean(conv_only$frmsize)
mean(atleast_1org$frmsize)

```

# Farm size -- Ashley's workflow
```{r message=FALSE, warning=FALSE}

# Collapse data to permit year so one obs per farm-year with total HA
farmsizes = final_data %>% # Get all data
    # filter(!is.na(soil_quality)) %>% 
    # filter(family != "") %>% 
    arrange(permit,year) %>% 
    group_by(permit,year) %>% # Collapse to permit-year
    summarise(avgOrg = avgOrg[1], ## First avgOrg obs for permit-year. Get same results with mean
              org = mean(pur_cdfa_org), ## First avgOrg obs for permit-year
              farmsize=mean(farmSz), ## Mean farm size
              .groups='keep') %>% 
    ungroup() %>% # ungroup
    group_by(permit) %>% # Regroup to collapse on permit alone
    summarise(frmsize = mean(farmsize),
              org = mean(org)) # mean of farm size at farm-level across all years


summary(farmsizes$frmsize[farmsizes$org > 0])
summary(farmsizes$frmsize[farmsizes$org == 0])

#######

####### Filter in another way #######

conventional_only_permits = final_data %>%
  filter(avgOrg == 0)

conventional_only_permits <- unique(conventional_only_permits$permit)
conv_farmsizes <- filter(farmsizes, permit %in% conventional_only_permits)
cat("\n")
noquote("All conventional summary")
print(summary(conv_farmsizes$frmsize))
cat("\n")
noquote("All conventional SD"); print(sd(conv_farmsizes$frmsize))
cat("\n")
cat("\n")
noquote("---")

cat("\n")
cat("\n")

atleastoneorg_permits <- final_data %>%
  filter(avgOrg != 0)

atleastoneorg_permits <- unique(atleastoneorg_permits$permit)
al1org_farmsizes <- filter(farmsizes, permit %in% atleastoneorg_permits)
noquote("some org summary")
summary(al1org_farmsizes$frmsize)
cat("\n")
noquote("some org SD")
sd(al1org_farmsizes$frmsize)

# Check that there is no overlap in these two permit sets
# intersect(conventional_only_permits, atleastoneorg_permits)

```

