---
title: "All Crop Summary Stats"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**The purpose of this Rmarkdown file is look at descriptive statistics of all crop fields in Kern County to get a broad overview of differences between conventional and organic agriculture fields. Values for the following categories are determined and put into an output table: **  
      * Total number of fields (total_fields)
      * Total hectares (total_hectares)
      * Average Field Size (average_field_size)
      * Average Soil Quality based on the Storie Index Rating (average_soilQ)
      * Total Active Ingredient/Pesticide Application (total_pest_app)
      * Average Kg per hectare application of active ingredients (kg_per_hectare)

***

Notes:

- This document and output are the same as in "7a_AllCrops_SummaryStats", except that the input for this file includes organic fields identified by the CDFA APN *AND* Kern Ag Shapefile attribute table ("ORGANIC" in the comm name)

#### 1. Load packages, set working directory, and prevent scientific notation
```{r packages_settings}

library(rgdal)
library(sf)
library(tidyverse)
library(reshape2)

options(scipen = 9999)
setwd("~/Desktop/Organics_Final/Working/R_files/Rmarkdown")
```

#### 2. 
```{r read_in_shapefiles}

# Values for for() loop
years = 2017

# Read in KernAg_CDFA_join shapefile data for specified years and convert to spatial data.frame 
for(i in years){
    
    # Read in shapefile for year i and buffer width j
    tmp = readOGR("../R_output/spatial/final_organics_data/") %>% 
      st_as_sf()
 
    # Assign a name to the dataframe
    assign(paste0("allOrgs_",i),tmp)
    
    # Get rid of the 'tmp' dataframe
    remove(tmp)
}


```

#### 3. Find organic crop types that have at least 5 fields/sites
```{r top_organic_crops}

topCrops_df = allOrgs_2017 %>% 
  as.data.frame() %>% # Convert to data.frame
  dplyr::select(-geometry) %>% # Remove geometry column
  group_by(comm_dt) %>% # Group by COMM column
  summarise(total_orgFields = sum(organic)) %>% # Sum the CDFA column. This tells us how many organic fields of each crop type there are
  arrange(-total_orgFields) %>% # Sort the table in descending order of number of fields per crop type
  filter(total_orgFields >= 10) # Get rid of crops with fewer than ten fields

comparison_crops = topCrops_df$comm_dt # Create a new vector with names of crops with at least five fields
comparison_crops # Display in an Rmarkdown document
```


#### 4. Summary stats of all fields, conventional or organic, that contain one of the 19 crops listed above
```{r all_fields}

all_fields = allOrgs_2017 %>% 
 as.data.frame() %>% 
 dplyr::select(-geometry) %>% 
 filter(comm_dt %in% comparison_crops) %>% 
 summarise(total_fields = n(),
           total_hectares = round(sum(hectars),1),
           average_field_size = mean(hectars, na.rm = T),
           avg_soil_q = mean(soil_q),
           total_pest_app = sum(KgPstAI),
           kg_per_hectare = mean(kgperhc))
     

```

#### 5. Organic Field Summary Stats
```{r org_sum_stats}

organic_fields = allOrgs_2017 %>% 
 as.data.frame() %>% 
 dplyr::select(-geometry) %>% 
 filter(comm_dt %in% comparison_crops) %>% 
 filter(organic == 1) %>% 
 summarise(total_fields = n(),
           total_hectares = round(sum(hectars),1),
           average_field_size = mean(hectars, na.rm = T),
           avg_soil_q = mean(soil_q),
           total_pest_app = sum(KgPstAI),
           kg_per_hectare = mean(kgperhc))

```

#### 6. Conventional Field Summary Stats
```{r conv_sum_stats}

conv_fields = allOrgs_2017 %>% 
       as.data.frame() %>% 
       dplyr::select(-geometry) %>% 
       filter(comm_dt %in% comparison_crops) %>% 
       filter(organic == 0) %>% 
 summarise(total_fields = n(),
           total_hectares = round(sum(hectars),1),
           average_field_size = mean(hectars, na.rm = T),
           avg_soil_q = mean(soil_q),
           total_pest_app = sum(KgPstAI),
           kg_per_hectare = mean(kgperhc))

```

#### 7. Combine summary tables into one. Remove '#' to write output CSV
```{r}

tmp = rbind(all_fields, conv_fields,organic_fields)
rownames(tmp) = c("All","Conv","Org")
     
write.csv(tmp,"../R_output/CSV/SummaryStatistics/AllFields_CDFA_KernAG")
```

